### 2024-03-10 chapter_3/src/chapter_3.qmd
trying out the models a bit

# Load the functions
box::use(
    datasummary[...]
)

```

@@

[Study 1](#study-1) seeks to address $H_1$ and $H_2$. In [Study 1](#study-1), I recruit participants from ***[YouGov/Qualtrics/Whatever online panels are in vogue that week]***. First, I ask participants several questions about their demographic background (i.e., age, gender identity, education, and income). I additionally present them with a battery to measure conflict avoidance as potential confounds.

@@

To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1). I will fit a logistic regression to examine whether there are differences in the outcome depending on this prime.

>>>>

# Load the functions
box::use(
  DBI[dbConnect, dbGetQuery],
  modelsummary[datasummary_skim]
)

# Connect to the db
con <- dbConnect(
  duckdb::duckdb(),
  dbdir = "./chapter_3/data/clean/study_1.db",
  read_only=TRUE
)

# Load the data
df_descriptives <- dbGetQuery(
  con,
  "
  SELECT
    Age,
    Gender AS 'Gender (Male, Female, Non-Binary, Other)',
    Education,
    White,
    Attention,
    Dem3 AS 'PID (Republican, Independent, Democrat)',
    DislikeArgue AS 'Dislike Arguing',
    EnjoyChallenge AS 'Enjoy Challenging'
  FROM 
    Clean;
  "
)
df_primed <- dbGetQuery(con, "SELECT * FROM Clean WHERE CorrectColor=1 AND PoliticalPrime == 1;")
```

@@

[Study 1](#study-1) seeks to address $H_1$ and $H_2$. In [Study 1](#study-1), I recruit participants from YouGov in a module of the Congressional Election Study. First, I ask participants several questions about their demographic background (i.e., age, gender identity, education, and income). I additionally present them with a battery to measure conflict avoidance as potential confounds. @tbl-descriptive-demo presents the basic demographics of my participants.

```{r}
#| label: tbl-descriptive-demo
#| tbl-cap: Descriptive statistics of sample
#| echo: false
datasummary_skim(data=df_descriptives)
```

@@

### Results

To address $H_1$, the outcome variable of interest is whether or not people notice the color of the shirt (0 or 1,) as explained by whether they received the political prime or not (0 or 1). To measure whether participants notice the color of the shirt, I ask them to report what the color of the shirt was. I then compare that to the color of the shirt that they actually saw. Those who reported the correct color received a value of 1 and those who were incorrect received a value of 1. I fit a logistic regression to examine whether there are differences in the outcome depending on this prime.

- Do people notice color when they are in the political prime v not
- Do people who are conflict avoidant notice the color of shirt or not?
